The problem and promise of scale in multilayer networks

### 2020-01-21 paper/manuscript.Rmd
update rmd
add perspective subheaders
Merge branch 'master' of https://gitlab.com/robit.a/scale-in-multilayer-networks.git
Conflicts:
	paper/manuscript.Rmd
	paper/manuscript.md
collective move

>>>>

## Perspectives  to advance multilayer networks

### Landscape ecology

### Individual fitness and phenotypes

### Movement ecology and collective movement

Animal movement undoubtedly affects the social environment (Strandburg-Peshkin et al. 2015) and multilayer networks are no exception (Mourier et al. 2019). Movement is a dynamic process and is related to an individual’s space use as well as the resources consumed within their home range (Van Moorter et al. 2016). Collective movement can reduce group-level predation via detection-dilution trade-offs, while it can also improve information transfer about the quality or location of resources (Jolles et al. 2019). Social processes, movement decisions, and space use are therefore inextricably linked.

Although multilayer animal social networks are relatively novel (Silk et al. 2018), integrating movement behaviour within multilayer networks has not yet been widely applied. In gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate *monolayer* association networks within a multilayer network (Papageorgiou et al. 2019). In addition, *spatial networks* are networks of locations, which are connected in a network when individuals move between locations. For example, spatial networks were applied to monitor movement of sharks between fixed location autonomous arrays, where nodes represent locations within the array, *intralayer edges* represent individual movement frequency, and *interlayer edges* represent contact probability among individuals at a given node (Mourier et al. 2019). While both studies integrate movement in some capacity, neither generate networks based on continuous measures of collective, or dyadic, movement (Long et al. 2014).

	Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make movement decisions in the context of their local environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A collective movement layer could constitute similarity in movement for dyads (Long et al. 2014) or groups (Bode et al. 2011) as well as at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse (global migration: Flack et al. 2018) scales. Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al. 2018).
